Latentcor: An R Package for Latent Correlation Estimation

### 2021-06-03 paper/paper.Rmd
typo

---
title: 'Latentcor: An R Package for Latent Correlation Estimation'
tags:
- R
- Statistics
- Latent Correlation
date: "18 May 2021"
output:
  rticles::joss_article: default
  rticles::joss_article(): default
authors:
- name: Mingze Huang
  orcid: 0000-0003-3919-1564
  affiliation: 1, 2
- name: Irina Gaynanova
  orcid: 0000-0000-0000-0000
  affiliation: 2
- name: Christian L. Muller
year: 2021
bibliography: paper.bib
affiliations:
- name: Department of Statistics, Texas A& M University
  index: 1
- name: Department of Economics, Texas A& M University
  index: 2
- name: Department of Statistics, University of Munich
  index: 3
csl: apa.csl
journal: JOSS
---

>>>>

---
title: 'Latentcor: An R Package for Latent Correlation Estimation'
tags:
- R
- Statistics
- Latent Correlation
date: "18 May 2021"
output:
  rticles::joss_article: default
authors:
- name: Mingze Huang
  orcid: 0000-0003-3919-1564
  affiliation: 1, 2
- name: Irina Gaynanova
  orcid: 0000-0000-0000-0000
  affiliation: 2
- name: Christian L. Muller
year: 2021
bibliography: paper.bib
affiliations:
- name: Department of Statistics, Texas A& M University
  index: 1
- name: Department of Economics, Texas A& M University
  index: 2
- name: Department of Statistics, University of Munich
  index: 3
csl: apa.csl
journal: JOSS
---

### 2021-06-03 paper/paper.tex
typo

\begin{Shaded}
\begin{Highlighting}[]
\NormalTok{X1 }\OtherTok{\textless{}{-}}\NormalTok{ simdata}\SpecialCharTok{$}\NormalTok{X1; X2 }\OtherTok{\textless{}{-}}\NormalTok{ simdata}\SpecialCharTok{$}\NormalTok{X2; Sigma12\_tt }\OtherTok{\textless{}{-}}\NormalTok{ simdata}\SpecialCharTok{$}\NormalTok{Sigma12}
\CommentTok{\# Estimate latent correlation matrix with original method}
\NormalTok{R1\_tt\_org }\OtherTok{\textless{}{-}} \FunctionTok{estR}\NormalTok{(X1, }\StringTok{"binary"}\NormalTok{, }\AttributeTok{method =} \StringTok{"original"}\NormalTok{)}
\NormalTok{R2\_tt\_org }\OtherTok{\textless{}{-}} \FunctionTok{estR}\NormalTok{(X2, }\StringTok{"continuous"}\NormalTok{, }\AttributeTok{method =} \StringTok{"original"}\NormalTok{)}
\NormalTok{R12\_tt\_org }\OtherTok{\textless{}{-}} \FunctionTok{estR}\NormalTok{(X1, }\AttributeTok{type1 =} \StringTok{"binary"}\NormalTok{, X2, }\AttributeTok{type2 =} \StringTok{"continuous"}\NormalTok{,}
                              \AttributeTok{method =} \StringTok{"original"}\NormalTok{)}\SpecialCharTok{$}\NormalTok{R12}
\CommentTok{\# Estimate latent correlation matrix with original method}
\NormalTok{R1\_tt\_org }\OtherTok{\textless{}{-}} \FunctionTok{estR}\NormalTok{(X1, }\StringTok{"binary"}\NormalTok{, }\AttributeTok{method =} \StringTok{"approx"}\NormalTok{)}
\NormalTok{R2\_tt\_org }\OtherTok{\textless{}{-}} \FunctionTok{estR}\NormalTok{(X2, }\StringTok{"continuous"}\NormalTok{, }\AttributeTok{method =} \StringTok{"approx"}\NormalTok{)}
\NormalTok{R12\_tt\_org }\OtherTok{\textless{}{-}} \FunctionTok{estR}\NormalTok{(X1, }\AttributeTok{type1 =} \StringTok{"binary"}\NormalTok{, X2, }\AttributeTok{type2 =} \StringTok{"continuous"}\NormalTok{,}
                              \AttributeTok{method =} \StringTok{"approx"}\NormalTok{)}\SpecialCharTok{$}\NormalTok{R12}
\end{Highlighting}
\end{Shaded}

>>>>

\begin{Shaded}
\begin{Highlighting}[]
\NormalTok{X1 }\OtherTok{\textless{}{-}}\NormalTok{ simdata}\SpecialCharTok{$}\NormalTok{X1; X2 }\OtherTok{\textless{}{-}}\NormalTok{ simdata}\SpecialCharTok{$}\NormalTok{X2; Sigma12\_tt }\OtherTok{\textless{}{-}}\NormalTok{ simdata}\SpecialCharTok{$}\NormalTok{Sigma12}
\CommentTok{\# Estimate latent correlation matrix with original method}
\NormalTok{R1\_b\_org }\OtherTok{\textless{}{-}} \FunctionTok{estR}\NormalTok{(X1, }\StringTok{"binary"}\NormalTok{, }\AttributeTok{method =} \StringTok{"original"}\NormalTok{)}
\NormalTok{R2\_c\_org }\OtherTok{\textless{}{-}} \FunctionTok{estR}\NormalTok{(X2, }\StringTok{"continuous"}\NormalTok{, }\AttributeTok{method =} \StringTok{"original"}\NormalTok{)}
\NormalTok{R12\_bc\_org }\OtherTok{\textless{}{-}} \FunctionTok{estR}\NormalTok{(X1, }\AttributeTok{type1 =} \StringTok{"binary"}\NormalTok{, X2, }\AttributeTok{type2 =} \StringTok{"continuous"}\NormalTok{,}
                              \AttributeTok{method =} \StringTok{"original"}\NormalTok{)}\SpecialCharTok{$}\NormalTok{R12}
\CommentTok{\# Estimate latent correlation matrix with original method}
\NormalTok{R1\_b\_approx }\OtherTok{\textless{}{-}} \FunctionTok{estR}\NormalTok{(X1, }\StringTok{"binary"}\NormalTok{, }\AttributeTok{method =} \StringTok{"approx"}\NormalTok{)}
\NormalTok{R2\_c\_approx }\OtherTok{\textless{}{-}} \FunctionTok{estR}\NormalTok{(X2, }\StringTok{"continuous"}\NormalTok{, }\AttributeTok{method =} \StringTok{"approx"}\NormalTok{)}
\NormalTok{R12\_bc\_approx }\OtherTok{\textless{}{-}} \FunctionTok{estR}\NormalTok{(X1, }\AttributeTok{type1 =} \StringTok{"binary"}\NormalTok{, X2, }\AttributeTok{type2 =} \StringTok{"continuous"}\NormalTok{,}
                              \AttributeTok{method =} \StringTok{"approx"}\NormalTok{)}\SpecialCharTok{$}\NormalTok{R12}
\end{Highlighting}
\end{Shaded}
